\documentclass[a4paper]{article}

\usepackage{fullpage} % Package to use full page
\usepackage{parskip} % Package to tweak paragraph skipping
\usepackage{tikz} % Package for drawing
\usepackage{amsmath}
\usepackage{hyperref}

\title{MTH 4300: Algorithms, Computers, and Programming II}
\author{HW \#2}
\date{Due Date: October 3rd, 2024}

\begin{document}
\maketitle

% \section{Note}
\textbf{Inside of git repo check under folder hw\_solutions you can find a file named hw2\_template.cpp to help guide you}

\section{Implement a Dynamic 2D Array (Matrix) Using Pointers}
Write a C++ program to dynamically create a 2D array (matrix) of integers of size m x n using dynamic memory allocation. You should:
\begin{itemize}
    \item Ask the user to input the number of rows (m) and columns (n).
    \item Dynamically allocate memory for the 2D array.
    \item Initialize the 2D array with some values (e.g., fill with consecutive numbers).
    \item Print the matrix to the console.
    \item Deallocate the memory properly after use to avoid memory leaks.
    \item Handle edge cases where the user might input invalid sizes (like 0 or negative values).
\end{itemize}


\section{Recursion}
Write a recursive function to compute the sum of all elements in an array of integers, 
the input parameters to the function should just be the array of any size, and the function should return 
the sum as an int. Note, I will test your function with arrays of different sizes. \
No user input is required for this question.


\section{Arrays}
You are given two arrays of integers, arr1 and arr2, each of size n.
Write a C++ function that checks if arr2 is a rotation of arr1. For 
example, if arr1 = \{1, 2, 3, 4, 5\} and arr2 = \{3, 4, 5, 1, 2\}, then arr2
is a rotation of arr1. The input parameters to the function should be 
the two int arrays of any size n and you should return a bool, true if it
is a rotation and false otherwise. Note, I will test your function with arrays of different sizes.
No user input is required for this question.



\end{document}