\documentclass[a4paper]{article}

\usepackage{fullpage} % Package to use full page
\usepackage{parskip} % Package to tweak paragraph skipping
\usepackage{tikz} % Package for drawing
\usepackage{amsmath}
\usepackage{hyperref}

\title{MTH 4300: Algorithms, Computers, and Programming II}
\author{Fall 2024}
\date{Midterm}

\begin{document}
\maketitle


\section{TRUE OR FALSE}
\begin{enumerate}
    \item A stack overflow is when you run out of memory on the heap
    \item An attribute refers to a variable defined inside a class
    \item Is this correct syntax: string a = 'apple';
    \item = and == are the same thing in c++
    \item Will this for loop ever halt: for(int i =0; i < 10; i=i+3)
    \item You can change the size of an array more than once.
    \item A pointer is allowed to store another pointer
    \item A compiler is used to move files from one directory to another
    \item The command cp list all the files in the current working directory
    \item Is this syntax correct:
    \begin{verbatim}
      int a =5;
      int* p = a;  
    \end{verbatim}    
\end{enumerate}

\textbf{Solutions:}
\begin{enumerate}
      \item F
      \item T
      \item F
      \item F
      \item T
      \item F
      \item T
      \item F
      \item F
      \item F
\end{enumerate}
\newpage


\section{SHORT ANSWER}
\begin{enumerate}
    \item Fix the function below:
    \begin{verbatim}
      int my function(int param1, int param2)
      {
      cout<<parm2<<endl;
      double param3 = param1/param2;
      return param3;  
    \end{verbatim}
    
    }
    \item Whats a memory leak and how is it caused.
    \item Your cpu can only read what type of files? (the answer is not an extension like .out)
    \item Name one reason why docker is useful
    \item What is 49\%5 equal to?
    \item What is the main difference between a struct and a class?
    \item What is the negation operator for boolean statements?
    \item Write the code to create a 2d array on the heap.
    \item What does new do?
    \item In recursion, if you do not define , then the recursive function will never stop.
    
\end{enumerate} 
\newpage


\section{CODING} 
\begin{enumerate}
    \item Write a c++ class to describe a dragon. Make sure to include at least 3 attributes(set to private),
    3 methods(set to public), and a constructor(set to public). Write a main function and create 2
    objects in the main. Figure out a way to print one of your attributes in the main by calling one of
    your methods.
    \item Ask the user to input the size of an array, then create a 1d array on the heap, such that for each
    index you store the (index + 1). So at index 0 it should store 1, index 1 should store 2 and so
    forth. Write a recursive function that computes the sum of only the odd indices. The function
    should work for arrays of any size.
\end{enumerate} 

\textbf{Solutions:}
\begin{enumerate}
  \item \href{run:./test_coding_question1.cpp}{coding\_question1.cpp}
  \item \href{run:./test_coding_question2.cpp}{coding\_question2.cpp} 
\end{enumerate}

\end{document}